% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ %
% Author:  Sean Anastasi <spa@cs.washington.edu>                               %
% Version: 2010/5/3                                                            %
% ~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ %
\documentclass[9pt]{article}

\usepackage{fullpage, multicol}
\usepackage[latin1]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\renewcommand*\familydefault{\sfdefault} % Font family
\renewcommand{\labelitemi}{$-$}          % List items are dashes.

% Force 8.5x11 paper and margins.
\pdfpagewidth    8.5in
\pdfpageheight   11in 
\textheight      11in
\textwidth       6.9in
\topmargin      -0.0in
\oddsidemargin  -0.4in
\pagestyle{empty}
\raggedright
\setlength{\tabcolsep}{0in}

\newcommand{\mysectiontitle}[1]{ { { \large{\textbf{#1} } } \vspace{0.02in}} }
\newcommand{\secspace}{\vspace{0.5cm}}
\newcommand{\smallvspace}{\vspace{0.1cm}}

% Hack, use lists to indent temporarily.
\newenvironment{changemargin}[2]{%
  \begin{list}{}{%
    \setlength{\topsep}{0pt}%
    \setlength{\leftmargin}{#1}%
    \setlength{\rightmargin}{#2}%
    \setlength{\listparindent}{\parindent}%
    \setlength{\itemindent}{\parindent}%
    \setlength{\parsep}{\parskip}%
  }%
  \item[]}{\end{list}}

\begin{document}
  %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  % HEADER
  %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
  \begin{multicols}{2}
    {\huge{\textbf{Sean P. Anastasi}}}
    \begin{changemargin}{1cm}{0cm}
      \textit{spa@cs.washington.edu} \textit{spa@u.washington.edu} \\

      \hfill 5215 15th Ave NE \\
      \hfill Seattle, WA 98105 \\
      \hfill \textit{(240) 447-3083} \\
    \end{changemargin}
      
  \end{multicols}
  
  \begin{changemargin}{1cm}{0.5cm}
    %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    % EDUCATION & AWARDS
    %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    \begin{multicols}{2}
      \mysectiontitle{Education}
      \vspace{-0.5em}
      \begin{changemargin}{0.5cm}{0.5cm}
      University of Washington \\
      Major: Computer Science \\
      Major GPA   3.68 \\
      Overall GPA 3.33 \\
      \end{changemargin}
      \vspace{1em}
    
      \mysectiontitle{Honors and Awards}
      \vspace{-0.5em}
      \begin{itemize}
        \itemsep -1px
        \item Eagle Scout Award
        \item Dean's list Aut. 2006, Aut. 2007
        \item Glerum Endowed Scholarship \\ (CSE Departmental Scholarship)
      \end{itemize}
    \end{multicols}

    \vspace{-0.5em}\smallvspace
    %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    % WORK EXPERIENCE
    %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    \mysectiontitle{Work Experience}
    \begin{changemargin}{0.5cm}{0.5cm}
      {\textbf{Amazon.com, Inc.}}, Seattle, WA \hfill \textit{Jun., 2009 - Sept. 2009} \\
      \textit{Software Development Engineer Intern} \\
      Designed and implemented a production system for quantity limits on items
      and a system to automatically set those limits on items sold at a loss.
    
      \smallvspace
      {\textbf{University of Washington CSE}}, Seattle, WA \hfill \textit{Jan., 2008 - Present} \\
      \textit {Undergraduate Teaching Assistant}           CSE 142 (Introductory Computer Science I)
      \phantom{\textit{Undergraduate Teaching Assistant}} CSE 341 (Programming Languages)           \\
      Taught a one hour section of 20-30 students, taught in the Introductory Programming 
      Laboratory, graded homework and exams and developed  classroom material and grading criteria.
  
      \smallvspace
      {\textbf{Government Employees Insurance Company (GEICO)}}, Chevy Chase, MD \hfill \textit{Jul., 2007 - Sept., 2007} \\
      
      \textit{Web Design Intern} \\
      Worked on projects within the Underwriting and Project Management
      department to improve GEICO's intranet. \\
      \begin{itemize}
        \item Translation of page data from HTML to XML-based structure. Developed XML schemas and DTDs.
        \item Improved departmental web development skills in HTML, XML and XSLT.
      \end{itemize}
    \end{changemargin}
    
    
    \vspace{0.5em}
    %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    % AREAS OF STUDY/ PROJECTS
    %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    \mysectiontitle{Areas of Study/ Projects}
    \vspace{-0.5em}
    \begin{multicols}{2}    
      \begin{itemize}
        \itemsep -1px
        \item Digital Design, Assembly Language, Embedded Systems Design
        \item Formal Semantics, Compiler Design
        \item Computer Graphics
        \item Website Design - Designed and built webpages for several student organizations
        \vspace{0.5em}
        \item Operating Systems - Modified the Linux and Windows Server kernel, FAT file system in class projects.
        \item Computer Vision, Artificial Intelligence, Embedded Systems - Designed, built and programmed autonomous, maze-solving 
              robot on an embedded Linux system.
      \end{itemize}
    \end{multicols}
    
    
    \vspace{-0.5em}
    %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    % UNDERGRADUATE RESEARCH
    %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    \mysectiontitle{Undergraduate Research}
    \begin{changemargin}{0.5cm}{0.5cm}
      {\textbf{MobileASL}} \hfill \textit{Jan., 2008 - Present} \\
      
      \textit{http://mobileasl.cs.washington.edu} \\
      Video compression to enhance intelligibility of Sign Language communication. Worked on porting the application from Windows Mobile 
      to a new, Linux-based phone.  Embedded linux development, network communication and media framework experience.
    \end{changemargin}
    
    
    \vspace{1em}
    %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    % RELEVANT SKILLS
    %~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
    \mysectiontitle{Relevant Skills}
    \begin{changemargin}{0.5cm}{0.5cm}
      Excellent computer skills and problem solving ability. Experience planning, organizing, and executing a project
      from start to finish.  Ability to learn new skills very quickly and immediately use them effectively.
  
      Experience with programming, debugging, graphics, hardware, and networking in Linux, Windows Vista/XP/2000.
  
      Proficiency in a large number of programming languages including Java, C, Ruby and Python.
      Considerable experience with web design and languages such as HTML, Javascript, Ruby on Rails, PHP and ASP. 
      Experience with many other languages including C++/C\#, Perl, Scheme, Haskell, etc.
  
      Some ability in Japanese, Swedish and Spanish.
    \end{changemargin}
  \end{changemargin}
\end{document}

